Joker: A Unified Interaction Model For Web Customization

### 2021-08-05 paper.tex
Remove page header boilerplate
Remove reference to cognitive dimensions in abstract

\settopmatter{printfolios=true}
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

@@

  To illustrate our unified interaction model, we have implemented a
  tool called Joker which is an extension of Wildcard, a prior web
  customization system. Through case studies, we show that Joker can be
  used to customize many real-world websites. We also present a
  formative user study with five participants, which showed that people
  with a wide range of technical backgrounds can use Joker to customize
  websites, and also revealed some interesting limitations of our
  approach. Finally, we present a heuristic evaluation of our design
  using the Cognitive Dimensions framework.
 \end{abstract}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

Our wrapper induction algorithm implements a set of heuristics inspired by Vegemite
as described below:

>>>>

\settopmatter{printfolios=true}
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}

@@

  To illustrate our unified interaction model, we have implemented a
  tool called Joker which is an extension of Wildcard, a prior web
  customization system. Through case studies, we show that Joker can be
  used to customize many real-world websites. We also present a
  formative user study with five participants, which showed that people
  with a wide range of technical backgrounds can use Joker to customize
  websites, and also revealed some interesting limitations of our
  approach.
 \end{abstract}

@@

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle
\pagestyle{plain}

@@

Joker's wrapper induction algorithm implements a set of heuristics inspired by Vegemite
as described below:
